% !TeX program = pdflatex
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[version=4]{mhchem}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Nassar Shakir} \\ \vspace{1pt}
    \small 613-876-2554 $|$ 
    \href{mailto:nshak072@uottawa.ca}{\underline{nshak072@uottawa.ca}} $|$ 
    \href{https://www.linkedin.com/in/nassar-shakir}{\underline{linkedin.com/in/nassar-shakir}} $|$
    \href{https://github.com/nshak072}{\underline{github.com/nshak072}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Bachelor of Applied Science in Chemical Engineering}{Sept. 2021 -- May 2026}
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Bachelor of Science in Computing Technology}{Sept. 2021 -- May 2026}
\resumeSubHeadingListEnd

%-----------ENGINEERING PROJECTS-----------
\section{Engineering Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Vinyl Acetate Monomer Plant Design}{Jan. 2026 -- Present}
{University of Ottawa}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Designed and simulated an industrial-scale vinyl acetate monomer production facility.}
    \resumeItem{Conducted literature review and market analysis.}
    \resumeItem{Developed full Aspen HYSYS process flowsheet for reactor, heat integration, separation, and recycle streams.}
    \resumeItem{Sized and optimized plug flow reactor (PFR), heat exchanger, and distillation column.}
    \resumeItem{Performed economic feasibility studies and HAZOP safety analysis.}
\resumeItemListEnd

\resumeSubheading
{Process Control: Controller Design}{Sept. 2025 -- Dec. 2025}
{University of Ottawa}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Used Altair Embed to simulate controllers for a distillation column.}
    \resumeItem{Tuned controller parameters using Direct Synthesis method.}
\resumeItemListEnd

\resumeSubheading
{Reactor Design Project}{Sept. 2025 -- Dec. 2025}
{University of Ottawa}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Implemented adaptive Runge–Kutta–Fehlberg (RKF45) numerical method in VBA to simulate packed bed reactor (PBR) behavior.}
    \resumeItem{Optimized reactor performance using Excel-based simulations.}
\resumeItemListEnd

\resumeSubheading
{Renewable Methanol Production from \ce{CO2} and Green Hydrogen}{May 2025 -- Aug. 2025}
{University of Ottawa}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Designed 40,000 tonne/year methanol plant (99.5\% purity) using Aspen Plus.}
    \resumeItem{Developed full process flowsheet including reactor, separation units, and recycle streams.}
    \resumeItem{Performed mass and energy balances and preliminary equipment sizing.}
\resumeItemListEnd

\resumeSubheading
{Packed Absorption Tower Design and Optimization}{Jan. 2025 -- April. 2025}
{University of Ottawa}{Ottawa, ON}
  \resumeItemListStart
    \resumeItem{Designed and optimized a packed absorption column for 99\% ethanol recovery using HTU/NTU correlations.}
    \resumeItem{Selected packing type/size; determined column diameter and height.}
    \resumeItem{Evaluated pressure drop, cost, and operating conditions via Excel-based simulator.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------COMPUTER SCIENCE PROJECTS-----------
\section{Computer Science Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Stable Marriage Resident Matching Service}{Jan. 2026 -- Present}
{Java, Golang, Scheme, Prolog}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Implemented Gale–Shapley stable matching algorithm for medical resident allocation.}
    \resumeItem{Validated correctness through edge-case and stress testing.}
\resumeItemListEnd

\resumeSubheading
{LocalLoop – Community Events Android Application}{May 2025 -- Aug. 2025}
{Android Studio, Java, Firebase, GitHub}{Ottawa, ON}
\resumeItemListStart
    \resumeItem{Designed and developed Android application for managing and discovering community events.}
    \resumeItem{Implemented role-based access control (Admin, Organizer, Participant).}
    \resumeItem{Enabled event creation, editing, deletion with categories, dates, and fees.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
 \textbf{Simulation Software}: Aspen HYSYS, Altair Embed, Aspen Plus \\
 \textbf{Languages}: Java, Python, Golang, Scheme, Prolog, Firebase \\
 \textbf{Developer Tools}: Git, VS Code, Android Studio, IntelliJ
}}
\end{itemize}

\end{document}

